NOSQL\\ BEST PRACTICES

### 2018-04-15 pgconfus2018/presentation.tex
Update detoast latency graph, add note about JIT for deform
Remove jsonbc
Schema for fixed key, improved schema for deform

@@

        \vspace{1cm}
        \begin{tcolorbox}[adjusted title= Table]
        \begin{tabular}{c|c|c|c|c|c}
            \tikzmark{start} value & \tikzmark{right} value & value & value & value & value... \\\hline
        value & value & value & value & value & value... \\\hline
        \tikzmark{end} value & value & value & value & value & value...
        \end{tabular}
        \end{tcolorbox}

@@

        \begin{tikzpicture}[overlay,remember picture]
            \draw[line width=1mm, color=red, rounded corners]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(9.5,0.8)$) rectangle ($(\x1,\y2)+(12.0,-2.1)$);
        \end{tikzpicture}

        \vspace{1cm}
        \begin{tcolorbox}[adjusted title= Table]
        \begin{tabular}{c|c|c|c|c|c}
        \tikzmark{start} value... & \tikzmark{right} value & value & value & value & value \\\hline
        value... & value & value & value & value & value \\\hline
        \tikzmark{end} value... & value & value & value & value & value
        \end{tabular}
        \end{tcolorbox}

        \begin{tikzpicture}[overlay,remember picture]
            \draw[line width=1mm, color=red, rounded corners]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(-0.3,0.8)$) rectangle ($(\x1,\y2)+(2.3,-2.1)$);
        \end{tikzpicture}

@@

        \includegraphics[width=0.75\textwidth,center]{select_slice.png}

@@

        \begin{itemize}[label={\MVRightarrow}]
            \item jsquery
            \item postgres-json-schema
            \item is\_jsonb\_valid
            \item zson (jsonbc, custom compression methods WIP)
            \item jsonb\_explorer
        \end{itemize}

@@

        \vspace{1cm}
        \begin{flushleft}
            findJsonbValueFromContainer -> binary search

            \_id in a fixed position?
        \end{flushleft}

>>>>

    \end{center}
\end{frame}
\note{
    with JIT compilation tuple deform can be faster up to 2 times
}

        \vspace{1cm}
        \onslide<1,2,3,4>
        \begin{tcolorbox}[adjusted title= Table]
        \begin{tabular}{c|c|c|c|c|c}
            \tikzmark{start}value & \tikzmark{right} value & value & value & value & value... \\\hline
        value & value & value & value & value & value... \\\hline
        \tikzmark{end}value & value & value & value & value & value...
        \end{tabular}
        \end{tcolorbox}

        \onslide<2,3,4>
        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm, color=white]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(1.5,1.3)$) -- node[] {} ($(\x1,\y2)+(12.0,1.3)$);
        \end{tikzpicture}

        \onslide<3,4>
        \begin{tikzpicture}[overlay,remember picture]
            \draw[->, line width=1mm]
            let \p1=(start), \p2=(end) in ($(\x1,\y1)+(-1.2,0.2)$) -- node[] {} ($(\x1,\y2)+(-1.2,0.0)$);
        \end{tikzpicture}

        \onslide<4>
        \begin{tikzpicture}[overlay,remember picture]
            \draw[line width=1mm, color=red, rounded corners]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(9.3,0.8)$) rectangle ($(\x1,\y2)+(12.0,-2.1)$);
        \end{tikzpicture}

@@

        \vspace{1cm}
        \begin{tcolorbox}[adjusted title= Table]
        \begin{tabular}{c|c|c|c|c|c}
        \tikzmark{start}value... & \tikzmark{right} value & value & value & value & value \\\hline
        value... & value & value & value & value & value \\\hline
        \tikzmark{end}value... & value & value & value & value & value
        \end{tabular}
        \end{tcolorbox}

@@

        \begin{tikzpicture}[overlay,remember picture]
            \draw[line width=1mm, color=red, rounded corners]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(-0.3,0.8)$) rectangle ($(\x1,\y2)+(2.1,-2.1)$);
        \end{tikzpicture}

@@

@@

        \begin{itemize}[label={\MVRightarrow}]
            \item jsquery
            \item postgres-json-schema
            \item is\_jsonb\_valid
            \item zson (custom compression methods WIP)
            \item jsonb\_explorer
        \end{itemize}

@@

        \vspace{1.0cm}

        \only<1>{
            \begin{tikzpicture}
                \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
                \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {\textbf{\_id}};
                \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
                \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
                \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
                \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
                \draw[->, line width=0.75mm, color=white] (0,-0.5) to [controls=+(-90:2) and +(-90:2)]  (7,-0.5);
            \end{tikzpicture}
        }

        \only<2>{
            \begin{tikzpicture}
                \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
                \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {\textbf{\_id}};
                \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
                \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
                \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
                \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
                \draw[->, line width=0.75mm] (0,-0.5) to [controls=+(-90:2) and +(-90:2)]  (7,-0.5);
            \end{tikzpicture}
        }

        \only<3>{
            \begin{tikzpicture}
                \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
                \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {\textbf{\_id}};
                \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
                \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
                \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
                \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
                \draw[->, line width=0.75mm] (0,-0.5) to [controls=+(-90:2) and +(-90:2)]  (7,-0.5);
                \draw[->, line width=0.75mm] (7,-0.5) to [controls=+(-90:1) and +(-90:1)]  (5,-0.5);
            \end{tikzpicture}
        }

        \only<4>{
            \begin{tikzpicture}
                \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
                \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {\textbf{\_id}};
                \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
                \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
                \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
                \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
                \draw[->, line width=0.75mm] (0,-0.5) to [controls=+(-90:2) and +(-90:2)]  (7,-0.5);
                \draw[->, line width=0.75mm] (7,-0.5) to [controls=+(-90:1) and +(-90:1)]  (5,-0.5);
                \draw[->, line width=0.75mm] (5,-0.5) to [controls=+(-90:1) and +(-90:1)]  (3,-0.5);
            \end{tikzpicture}
        }
